Supplementary Information: Vulnerability of tree growth

### 2024-07-02 doc/manuscript.Rmd
manuscript edits

***Sites and data*** -

@@

>>>>

***Sites and data***

*Huai Kha Khaeng plot*
- location
- annual precipitation
- ecosystem type/association
- long-term trends from @vlam et al etc

*Resistance*
-Dendrometer band measurements - census protocol
-Calculated DBH at each instance from first DBH and window size using Condit's functions.
-Removed measures with large decimal errors, large outliers (> 3 SD). 
- For all individuals with three points of measurements for each drought, calculated raw increment as difference between relevant censuses to get pre-drought increment and drought-year increment.
- Resistance - difference between pre-drought and drought-year increment

*Tree size*
- calculated DBH for at the start of the pre-drought year from dendrometer band window

*Deciduousness*
-data from @williams_deciduousness_2008. 
-Leaf phenology score - mean proportion of crown loss. 
-Continuous scale from 1 to 4, where 4 is maximum crown loss or deciduousness. 
-One value per species. 
- 7 species out of the top 51 species in the dendroband census have no values. (currently excluded from analysis but can fill these with best estimates and add them back in)

*Exposure*
- crown illumination index for each individual, collected at each dendrometer band census
- categorical variable with values 1 to 5 where 1 is least exposed and 5 is most exposed

*Topographic Wetness Index*
- calculated from topography
- estimate of water availability at a location

@@

For individual stems, we modelled drought resistance as:

$$
resistance \sim size + exposure + deciduousness + water + size*exposure + deciduousness*exposure + size*deciduousness + (1|drought.year)
$$
